\bf Faster Neural Machine Translation Inference

### 2018-02-06 fast-beam/fast-beam.tex
fast beam paper

Fusing the softmax and beam search increase the speed of the output layer by 43\% for beam size 1, decreasing to 25\% for a beam of 10 when translating the Europarl dataset. This led to an overall increase in translation speed of up to 23\%, Figure~\ref{fig:beam-europarl}. Translation speed improved by up to 41\% when translating the OpenSubtitles dataset, Figure~\ref{fig:beam-opensubtitles}. Compared to translating the Europarl test st, Figure~\ref{fig:pie-time-europarl} in Section~\ref{sec:Introduction}, the amount of time taken by the output layer dominates translation time for the OpenSubtitles test set, Figure~\ref{fig:pie-time-opensubtitles}.

>>>>

Fusing the last 3 steps led to a substantial reduction in the time taken, especially for beam size of 1 where the softmax does not actually have to calculated, Table~\ref{tab:fused-breakdown-europarl} and ~\ref{tab:fused-breakdown-opensubtitles}. This led to an overall increase in translation speed of up to 23\% for the Europarl test set, Figure~\ref{fig:beam-europarl}, and up to 41\% for the OpenSubtitles test set, Figure~\ref{fig:beam-opensubtitles}.

The amount of time taken by the output layer dominates translation time for the OpenSubtitles test set, Figure~\ref{fig:pie-time-opensubtitles}.
